\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-14 paper.tex
Revise up to Sect. 4

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_{_{0}} = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b

@@

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_{_{G}}(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\section{Experimental Details}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-5}
  %\\[12pt]
  %\includegraphics[scale=0.6]{Images/DE1}

@@

In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the width, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Monolayers}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
wt) and ethanol (purity: 99.9 $ \%$ wt ) in a 3:7:1 volume ratio,
respectively. After the anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
  electrodo?} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Reflectance Measurement}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer.

To
calculate the complex refractive index $ \tilde{n}_{_{PS}} = n_{_
  {PS}} - ik_{_{PS}} $ of a porous layer with homogeneous porosity
and thickness with smooth interfaces to throughout the entire
structure, the more suitable is the adjustment procedure of the
experimental reflectance or transmittance spectrum, this is for the
theoretical part. In the case of the reflectance spectrum. The
corresponding theoretical calculations were carried using procedure
for single  smooth layer (monolayer).
 \begin{eqnarray}\label{Eq:ECMR}
R=\dfrac{r _ {_ {01}}r _ {_ {12}} e^{-2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{-2i\delta}}
\end{eqnarray}
where $ r_{_ {01}} $ y $ r_{_ {12}} $ are the Fresnel reflectance
coefficients at the interfaces $aire/PS$ y $PS/c-Si$ which are
defined in terms of their complex refractive index ($\tilde{n}_{_ {1}}
$, $\tilde{n}_{_ {2}} $ y $ \tilde{n}_{_ {3}} $), for them
$r_{_{ij}}=(\tilde{n}_{_{i}}\cos\theta_i-\tilde{n}_{_{j}}\cos\theta_j)/(\tilde{n}_{_{i}}\cos\theta_i+\tilde{n}_{_{j}}\cos\theta_j)$,
($j=i=0,1,2$), whilst $\delta=2\pi
d/\lambda\sqrt{\tilde{n}^2_{_{2}}-\tilde{n}^2_{_{1}}\sin \theta_1}$.
 To adjust the reflectance spectrum, the layer thickness is an input
 parameter in the Eq.\ref{Eq:ECMR}. The advantage of this method is
 the possibility of taking into account the interface roughness effect
 by including the Davies-Bennett factor in the coefficient of each
 Fresnel \cite{I17, I18, I19}, which represents the roughness of a
 Gaussian distribution.
\subsection{Morphological studies}
The morphologies of the etched porous layers (cross-sectional) was
observed using SEM Hitachi SU1510 scanning electron microscopes
(Hitachi High Technologies Canada, Inc., Toronto, Canada), the
thickness  and porosity  of each fabricated  film was measured.
 \subsection{Refraction Indices Monolayer of Porous Silicon GRIN }
Through the electrochemical anodization of c-Si wafers, Psi monolayers
were obtained. For the refractive index of each monolayer Psi
calcalated by ussing  Bruggeman effective medium theory, as we
consider that we have a homogeneous medium associated with effective
dielectric function \cite{I20}. This effective dielectric function is
related to the dielectric functions of the two media, consisting of
two materials (air and silicon), where it is assumed that all the
pores or islands of the bulk material experience an average electric
field; the equation is expressed as follows:
 \begin{eqnarray}\label{Eq:Brugg}
 p\dfrac{\varepsilon_{_{air}}-\varepsilon_{_{PS}}}{\varepsilon_{_{air}}+\varepsilon_{_{PS}}}+(1-p)\dfrac{\varepsilon_{_{Si}}-\varepsilon_{_{PS}}}{\varepsilon_{_{Si}}+
   \varepsilon_{_{PS}}}
 \end{eqnarray}
 where $ p $ is the volume fraction of air within the PS layer
 (porosity); $\varepsilon_{_{air}}$ is the dielectric function of air;
 $\varepsilon_{_{Si}}$ is the dielectric function of c-Si, and
 $\varepsilon_{_{PS}}$ represents the dielectric function of PS. The
 dielectric function is a complex number and is related to the complex
 refractive index ($\tilde{n} = n - ik$), which is made up of real and
 imaginary parts, as follows $\varepsilon=\tilde{n}^2$. Its real part
 ($ n $) represents the ordinary refractive index when no light
 absorption occurs. The imaginary part ($ k $) is known as the
 extinction coefficient. The extinction coefficient determines the
 absorption rate in the medium \cite{I21}. Porosity can be estimated
 using the Bruggeman approximation, from Eq. \ref{Eq:Brugg} provided
 that the dielectric functions of each component (air and c-Si) are
 known.

 \subsection{Fabrication  of Microcavities of Porous Silicon GRIN }
 A conventional way to fabricate the porous silicon microcavity (MC)
 is a defect with a mode located between two DBRs (Distributed Bragg
 Reflector). Alternate layers of high refractive index (H) and low (L)
 refractive index are obtained, satisfying the Bragg condition
 $n_{_{i}}d_{_{i}}=\frac{\lambda_{_{c}}}{4}$  where $ i = H, L $. The
 defect must meet the condition
 $n_{_{L}}d_{_{L}}=\frac{\lambda_{_{c}}}{2}$, and the MC has the
 following sequence: $$ (HL)_6 HH (LH )_6 $$
 Initial data for conventional design we use $\lambda_{_{c}}= 0.67 \mu
 m$, $n_{_{H}} =2,6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \mu m  $,
 $t_{_{H}}=35 s  $ and for $n_{_{L}}= 1,4$,  $P_{_{L}} =0.75$,
 $d_{_{L}}=0.117 \mu m  $, $t_{_{L}}=11 s  $. All of this data is for
 the $ 0 $ point of the sample that is located at one end of the
 sample just below the tip counter-electrode.\\
 Our proposal for the fabrication of porous silicon GRIN microcavities
 uses the same conditions for fabrications of porous silicon GRIN
 monolayers as in section 3.1, and taking the conventional data
 mentioned above. The porous silicon microcavities (PSMC) with
 gradient refractive index (GRIN), were manufactured with different
 current densities ranging from $ 6 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a
 current of $ 5 \ \ mA $, with high refractive index $n_{_{H}} \sim
 2,761 $ to $ 2,808 $ and porosities from $ 0.44 $ to $ 0.39 $. Also
 for $ 50  $ to $ 20 \ \ mA / cm ^ 2 $, current of $ 38 \ \ mA $, for
 low refractive index $n_{_{L}}\sim 1,448 $ to $ 2,267 $ and with the
 corresponding  porosities of $ 0.75 $ to $ 0.64 $. Using our
 calibration ratio to design GRIN structures,  the corresponding
 current density for each measurement point.

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[scale=0.4]{Images/MicrGrin}
	\caption{\emph{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{_{Hi}}$ and low (L) refractive index
            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
            is the monolayer thickness of $n_{_{Hi}}$ at that
            measurement point. Therefore,  $d_{_{i}}$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_{_{i}} =
            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
            (2d_{_{Hi}})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
the monolayer thickness of $n_{_{Hi}}$ at that measurement
point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_{_{i}} =
(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[scale=.5]{Images/MCGRIN2}
  \caption{\emph{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }}
  \label{fig:MCGRIN3}
\end{figure}

>>>>

We assume that our electrolytic cell has the shape of a
prism (see Fig. \ref{f:celda}) with a horizontal rectangular base of sides $a$ and $b$, and
filled with the electrolyte up to a height $c$. We assume that the
walls of the cell are insulating while the bottom is completely
covered with the sample, which is a which is an
electrically grounded good conductor. Within the electrolyte we position an electrode
which we assume is a thin conductor, insulated from the electrolyte
but for a small area near its tip, which we thus approximate as a
point current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{Prism shaped electrolytic cell with a rectangular base of
    sides $a$, $b$ filled with electrolyte up to a height $c$. The
    walls of the cell are insulating and the bottom is completely
    covered by the sample, which is assumed to be a good
    conductor. The tip of the electrode is a thin insulated wire with
    just the tip uncovered and located at $\bm r_0=(x_0,y_0,z_0)$ within the
    liquid.\notaL{Quité el tipo de letra del pie de figura. Que la pongan en la
      revista.}\notaL{En la punta pusiste dos esferas. Quítalas y sólo
    pon un puntito dorado del ancho del cable. Muestra que la base
    está aterrizada}\notaL{Indica el voltaje y la
    corriente}\notaL{Mejor pon una fuente de corriente en lugar de una
  fuente de voltaje}}
  \label{f:celda}
\end{figure}
Within the electrolyte the current density is
\begin{equation}
  \label{eq:j}
  \bm j=\sigma\bm E,
\end{equation}
with
$\sigma$ the conductivity, $\bm E=-\nabla\varphi$ the electric field,
and $\varphi$ the electric potential. For a
stationary situation\notaL{Latex usa nabla como el nombre de
  $\nabla$}
$\nabla\cdot \bm j = \sigma\nabla\cdot\bm E=0$. Thus, within the electrolyte,
\begin{equation}
  \label{eq:laplace}
\nabla^{2} \varphi=0.
\end{equation}
Consider now an arbitrary closed surface
$\mathcal S$
within the electrolyte that surrounds completely the tip of the
electrode. Integrating $ \bm j$ over this surface we obtain
\begin{equation}
  \label{eq:I}
\int_{\mathcal S'} d\bm a \cdot \bm j = -I,
\end{equation}
where the prime on $\mathcal S'$ means we remove from the surface a
very small hole through which the wire that feeds the current to the
electrode gets
through. Assuming the wire is narrower than any other relevant
distance in the system, we may interpret Eq. \eqref{eq:I} as an
integral over a closed surface of the current \eqref{eq:j} within the
electrolyte, ignoring the actual current within the wire. Thus
\begin{equation}
  \label{eq:gauss}
  \int_{\mathcal S} d\bm a \cdot \bm E = -\frac{I}{\sigma}
\end{equation}
Using Gauss's law, we interpret this equation as a source for the
potential in the form of a point charge
\begin{equation}
  q_0 = -\frac{I}{4 \pi \sigma}
\end{equation}
at the position $\bm r_0=(x_0, y_0, z_0)$ of the
tip of the electrode. Note that $q_0$ would be the total charge,
and it shouldn't be further screened through the permittivity of the
electrolyte.

@@

E_x(0, y ,z)= E_x(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b

@@

We consider first a system made of identical unit charges
ocuppying the positions $\bm R$ of a 2D Bravais lattice $\{\bm R\}$,
which we will take as a rectangular lattice with lattice parameters
$2a$ and $2b$, and lying, for the time being, at the $z=0$ plane.
The potential it produces obeys
\begin{equation}
  \label{eq:poissonRed}
  \nabla^2\varphi(\bm r)=-4\pi\sum_{\bm R}\delta(\bm r_\|-\bm
  R)\delta(z)=-\frac{4\pi}{A}\sum_{\bm G}e^{i\bm G\cdot\bm r_\|}\delta(z),
\end{equation}
where $\bm r_\|$ is the projection of the observation position $\bm
r=(x,y,z)$ onto the $xy$ plane,
$\delta(\ldots)$ is Dirac's delta function, $\{\bm G\}$ is the
reciprocal lattice defined through $e^{i\bm G\cdot\bm R}=1$ for all
$\bm R$ and $\bm G$, $A=4ab$ is the area of the unit cell
and we used the Fourier representation of the 2D
periodically repeated delta function. We introduce a 2D Fourier representation for
the potential \notaL{Checar consistencia entre phi y varphi en todos lados}
\begin{equation}
  \label{eq:phifourier}
  \phi(\bm r)=\sum_{\bm G}\phi_{\bm G}(z)e^{i\bm G\cdot\bm r_\|}
\end{equation}
where $\phi_{\bm G}(z)$ is the Fourier coefficient of the potential at
the height $z$. Substitution in Eq. \eqref{eq:poissonRed} yields the
ordinary differential equation \notaL{El signo estaba mal. Chécalo.}
 \begin{eqnarray}
 \frac{d^2}{dz^2}\phi_{\bm G}(z)-G^2\phi_G(z)=
   -\frac{4 \pi}{A} \delta(z),
 \end{eqnarray}
an homogeneous equation for $z\ne0$ which may be trivially
solved. After applying boundary conditions at $z=0$ and regularity
conditions at infinity, we obtain
\begin{equation}
  \label{eq:phiG}
  \phi_{\bm G}(z)=
  \begin{cases}
    -\dfrac{2\pi}{A}\abs{z}&\text{if }G=0,\\
    \dfrac{2 \pi}{AG}  e^{- G \abs{z}}&\text{if }G\neq 0.
  \end{cases}
\end{equation}
The case $G=0$ corresponds to the potential produced by a uniformly charged plane,
while the case $G\ne 0$ is the potential produced by a sinusoidal
charge density on a plane given by the
symmetric solution that decays exponentially as we get away from
the source plane. Substituting into Eq. \eqref{eq:phifourier} yields
\begin{eqnarray}
  \label{eq:phiG1}
 \phi(\bm r) = -\frac{2 \pi}{A}  \abs{z} +{\sum_{\bm G}}' \frac{2 \pi
   }{AG} e^{- G \abs{z}} e^{i \bm G\cdot\bm r_\|},
 \end{eqnarray}
where the prime indicates that the term $G=0$ should be ommited from
the sum.

@@

\section{Procedures}
\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{paper-3}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-4}\\[12pt]
  \includegraphics[width=.8\textwidth]{paper-5}
  % \\[12pt]
  % \includegraphics[scale=0.6]{Images/DE1}

@@

\notaL{Cambié el título, pues tienes una mezcla de experimento y
  teoría aquí}
In Fig. \ref{fig:DE1} we show a schematic representation of our
experimental setup to manufacture porous silicon with GRIN.
\notaL{Cambié las figuras}
As dicussed above, we fabricated an electrolytic cell with the shape of a
rectangular prism on the bottom of which we place a Si wafer which makes
electrical contact to a gold plate \notaL{Lo inventé; de qué material es
  el contacto bajo la muestra} which together make the anode. The
catode consists of a platinum wire insulated except for a small region
at its tip, which we take as a point current drain.
We also show a schematic drawing of the expected GRIN PS structures,
with a gradient in the porosity, and in the width, density and depth
of the resulting pores.

\subsection{Fabrication of PS  GRIN Single Layers}
We manufactured single layer PS structures through an electrochemical
anodization on a (100) $p$-type crystalline Si wafer
(resistivity 0.002 - 0.005 $ \Omega\,\text{cm}$), under galvanostatic
conditions. The process was performed at
room temperature,\notaL{Controlaste/mediste la temperatura?} with an
electrolytic mixture of aqueous hydrofluoric
acid (HF) (concentration: 48 $ \% $ wt), glycerol (purity: 99.8 $ \% $
wt) and ethanol (purity: 99.9 $ \%$ wt ) in a 3:7:1 volume ratio,
respectively. After the anodizing process, the samples were rinsed with
ethanol (purity: 99.9 $ \% $  wt). The electrolytic cell had the shape
of a rectangular prism as shown in Fig. \ref{fig:DE1}, with a base of
size $0.62\text{cm}\times2.03\text{cm}$) with an uncovered sample area
of $1.206\text{cm}^2$. \notaL{¿Cuáles fueron las coordenadas del
  electrodo?} We manufactured samples using a current $I=5\text{mA}$
which yielded current densities in the range
$j_\perp=2.5-6.0\text{mA}/\text{cm}^2$ and other smples using a larger
current $I=40\text{mA}$ corresponding to current densities in the
range $j_\perp=20-50\text{mA}/\text{cm}^2$. The cathode was a
platinum wire that with an approximate diameter of $0.5\text{mm}$.
\subsection{Morphological studies}
\notaL{Cambié el orden}
The morphologies of the etched porous layers were
observed using a Hitachi SU1510 scanning electron microscope (SEM)
with which we measured the thickness $d$ and the porosity $p$ of the
films at different positions along the sample from its top and side
views (Fig. \ref{fig:DE1}).

\subsection{Reflectance Measurement}
We measured the reflectivity spectra using a {\em Perkin Elmer Lambda 950}
UV-Vis-NIR spectrophotometer. For iterpretation of the data in the
case of a single PS layer we used
the standard formula \notaL{referencia} for three media air (0), PS
(1) and c-Si (2),
 \begin{eqnarray}\label{Eq:ECMR}
   R=\frac{r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}{1+r _ {_ {01}}r _ {_ {12}} e^{2i\delta}}
\end{eqnarray}
where $ r_{01} $ y $ r_{12}$ are the Fresnel reflectance
coefficients at the air/PS and PS/c-Si interfaces \notaL{referencias}
and $\delta=k_{PS}^\perp d$, where $k_{PS}^\perp$ is
the component of the wavevector perpendicular to the surface within
the porous layer of width $d$.
\notaL{Me tienes que explicar dónde y cómo usaste lo que mencionas en
  la siguiente frase:
The advantage of this method is
the possibility of taking into account the interface roughness effect
by including the Davies-Bennett factor in the coefficient of each
Fresnel \cite{I17, I18, I19}, which represents the roughness of a
Gaussian distribution.}
\subsection{Refraction Index of PS GRIN Single Layers}
The local refractive index $n_{PS}$ of the PS layer was calculated from its
porosity $p$ through
Bruggeman's effective medium theory \cite{I20} \notaL{Elegir y checar:
  varepsilon o epsilon para funciones dieléctricas}
\begin{eqnarray}\label{Eq:Brugg}
 p\frac{1-\varepsilon_{PS}} {1+\varepsilon_{PS}} + (1-p)
  \frac{\varepsilon_{\text{Si}} - \varepsilon_{PS}}
  {\varepsilon_{\text{Si}}+\varepsilon_{PS}}
\end{eqnarray}
where the porosity $p$ is the volume fraction of air within the PS
layer, $\varepsilon_{Si}$ is the dielectric function of c-Si, and
$\varepsilon_{PS}=n_{PS}^2$ is the dielectric function of the PS.
\notaL{Quité frases irrelevantes.}
\subsection{Fabrication  of GRIN PS Microcavities}
After characterizing the preparation of single PS GRIN layers, we
fabricated PS GRIN microcavities (MC) as specific defects between two distributed Bragg
mirrors  (DBR). Alternate quarter wavelength plates of high (H) and low (L)
refractive indices $n_i$ of widths $d_i$, $i=H,L$ were prepared satisfying the Bragg condition
$n_id_i=\frac{\lambda_c}{4}$ at a given design
wavelength $\lambda_c$ and at a position $A$ (Fig. \ref{fig:DE1} which
we chose as that directly below the point-like electrode. The defect
was chosen as a half-wavelength low index layer of width $d_d$ such that
$n_Ld_L=\lambda_c/2$, and the MC has the
following sequence: $(HL)_6HH(LH )_6$. \notaL{Hay algo mal. La
  película de $\lambda/2$ fue de alto o de bajo índice? En una parte
  dices una cosa y en otra otra. ¿Será $(HL)_jHLLH(LH)_6$? ¿O será
  $(LH)_6LL(HL)_6$? ¡Muy descuidado!}
We chose $\lambda_c= 0.67 \mu\text{m}$. For the high index layers we
chose a current $I_H=5\text{mA}$ which corresponded to a current density
$j_{HA\perp}= 6\text{mA}/\text{cm}^2$ below the tip \notaL{checar}, and yielded
$n_H =2.6$, corresponding to a porosity \notaL{P mayúscula
  es porosidad, o p minúscula. Checar consistencia} $P_H =0.46$, and a
width $d_H=0.066 \mu\text{m}$, which required an attack time of
$t_H=35 \text{s}$. The corresponding parameters for the low density
layers were $I_L=38\text{mA}$, $j_{LA\perp}=50\text{mA}/\text{cm}^2$, $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \mu \text{m}$, and $t_L=11 \text{s}$. For the rest of the
sample the current density, porosity, index of refraction and width
varied, yielding a GRIN MC.

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[scale=0.4]{Images/MicrGrin}
	\caption{\emph{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{Hi}$ and low (L) refractive index
            $n_{Li}$, where $N_H$ is the number of layers for
            $n_{Hi}$ and $N_L$ is the number of layers for
            $n_{Li}$. Then,  $d_{Hi}$ is the monolayer thickness
            of  $n_{Hi}$ at that measurement point and $d_{Li}$
            is the monolayer thickness of $n_{Hi}$ at that
            measurement point. Therefore,  $d_i$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_i =
            (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) +
            (2d_{Hi})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{Hi}$ and low (L) refractive index $n_{Li}$, where $N_{H}$
is the number of layers for  $n_{Hi}$ and $N_L$ is the number
of layers for $n_{Li}$. Then,  $d_{Hi}$ is the monolayer
thickness of  $n_{Hi}$ at that measurement point and $d_{Li}$ is
the monolayer thickness of $n_{Hi}$ at that measurement
point. Therefore,  $d_i$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_i =
(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$.
Initial data for conventional design we use  $\lambda_c= 0.67 \ \
\mu m$, $n_H =2.6$, $P_H =0.46$, $d_H=0.066 \ \ \mu m
$, $t_H=35 s  $ y para  $n_L= 1.4$,  $P_L =0.75$,
$d_L=0.117 \ \ \mu m  $, $t_L=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[scale=.5]{Images/MCGRIN2}
  \caption{\emph{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }}
  \label{fig:MCGRIN3}
\end{figure}
